---
title: "Metworx v 3.0.2 software listing"
output: github_document
---

```{r setup, include=FALSE}
.libPaths("lib")
knitr::opts_chunk$set(echo = FALSE)
```
```{r install-packages, eval=FALSE}
install.packages("jsonlite", lib="lib")
install.packages("stringr", lib="lib")
```

```{r load-libraries}
library(jsonlite)
library(stringr)
```


## Operating system

```{r os}
ubuntuv <- system("lsb_release -a", intern=TRUE)
writeLines(ubuntuv)
```


## R

R is a freeware statistical modeling language.

```{r R}
rv <- system("R --version", intern=TRUE)
writeLines(rv)
```

## Rstudio-server and rstudio deskop

Rstudio server is available as a webapp and rstudio desktop is available via the desktop.  Both are the open source versions (freeware) and require no license.
Rstudio server and rstudio desktop are set to match in version number.

```{r rstudio}
rstudiov <- system("rstudio-server version", intern=TRUE)
writeLines(rstudiov)
```

## PiranaJS

PiranaJS is available via a web application and requires a user provided license.

```{r piranajs}
piranajsv <- fromJSON("/opt/pirana/piranajs/current/package.json")$version
writeLines(piranajsv)
```


## Pirana Desktop

Pirana Desktop is available via the desktop and requires a user provided license.

```{r pirana-desktop}
piranav <- readLines("/opt/pirana/pirana/pirana.pl")
piranav <- piranav[grep("our \\$version|our \\$pirana_build", piranav)]
piranav <- str_extract(piranav, c("[[:digit:]]+.[[:digit:]]+.[[:digit:]]+", "[[:digit:]]+"))
piranav <- paste(c("Version:", "Build:"), piranav)
writeLines(piranav)
```


## gFortran

gFortran is a freeware compiler as part of the GNU compiler suite.

```{r gfort}
gfv <- system("gfortran --version", intern=TRUE)[1]
writeLines(gfv)
```


## IntelFortran

Intel Fortran is available and requires a user provided license.

```{r ifort, warning=FALSE}
ifv <- system2("ifort", "-v", stderr=TRUE)
writeLines(ifv)
```

## OpenBUGS

OpenBUGS is freeware Bayesian statistical modeling software.

```{r openbugs}
# openbugsv <- system("OpenBUGS", intern=TRUE)
openbugsv <- "OpenBUGS version 3.2.3 rev 1012"
writeLines(openbugsv)
```

## Stan

Stan is freeware Bayesian statstical modeling software.

```{r stan}
stanv <- installed.packages()["rstan","Version"]
writeLines(stanv)
```

## Python

Python is a freeware computer language.

```{r python, warning=FALSE}
pythonv <- system2("python","--version", stderr=TRUE)
writeLines(pythonv)
```

## PsN

PsN is freeware used for managing NONMEM job submission and Pharmacometric tasks.

```{r psn}
psnv <- system("which execute | xargs ls -l", intern=TRUE)
psnv <- str_extract(psnv, "[[:digit:]].[[:digit:]].[[:digit:]]")
writeLines(psnv)
```


## NONMEM

NONMEM (Icon) is modeling software that requires a user provided license.  NONMEM is installed on each AMI using both the gFortran and Intel compiler.  gFortran compiled installations have been appended with "gf":

```{r nonmem}
nmv <- list.dirs("/opt/NONMEM", recursive=FALSE)
writeLines(nmv)
```

## Grid Engine

Freeware HPC managment software.

```{r sge}
gev <- system("qstat -help", intern=TRUE)[1]
writeLines(gev)
```

## TexLive

Freeware document rendering software.

```{r texlive}
latexv <- system("pdflatex -v", intern=TRUE)[1]
writeLines(latexv)
```

## Subversion

Freeware version control software.

```{r svn}
svnv <- system("svn help", intern=TRUE)[2]
writeLines(svnv)
```

## Shiny pro

Shiny server pro is available via Envision using licenses provided by Metworx.

```{r shiny-server}
shinyv <- system("shiny-server", intern=TRUE)[1]
shinyv <- str_extract(shinyv, "v[[:digit:]].[[:digit:]].[[:digit:]].[[:digit:]]*")
writeLines(shinyv)
```

## SAS

SAS is available via the desktop and requires a user provided license.

```{r sas}
sasv <- basename(list.dirs("/usr/local/SASHome/SASFoundation/", recursive=F))
writeLines(sasv)
```

## Monolix

Lixoft Monolix is available via the desktop and requires a user provided license.

```{r monlix}
monolixv <- basename(list.dirs("/opt/monolix", recursive=FALSE))
monolixv <- monolixv[grep("onolix", monolixv)]
writeLines(monolixv)
```

## Matlab

Mathworks Matlab is available via the desktop and requires a user provided license.

```{r matlab}
matlabv <- system("which matlab | xargs ls -al", intern=TRUE)
matlabv <- str_extract(matlabv, "R[[:digit:]]+[[:alnum:]]*")
writeLines(matlabv)
```


## Git

Git is freeware version control software.

```{r git}
gitv <- system("git --version", intern=TRUE)
writeLines(gitv)
```

